### 2017-09-14 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
update

\textbf{Solution:}

>>>>

\textbf{Solution:}
Consider the intervals $E_k^i = [i\cdot2^-{k}, ~(i+1)2^{-k})$. Then
$$
T[E_k] = \bigcap_{i=1}^{2^k}F_{k_i},
$$
where 
$$
F_{k_i} = \left\{
\begin{aligned}
&[F_{k_{i-1}}.\text{left}, ~F_{k_{i-1}}.\text{mid}), ~\text{if}~ k_i = 0 \\
&[F_{k_{i-1}}.\text{mid}, ~F_{k_{i-1}}.\text{right}), ~\text{if}~ k_i = 1.
\end{aligned}
\right.
$$
Then since the finite intersection of closed sets is measurable, we know that $T[E_k]$ is measurable, and we have $m(T(E_k)) = m(E_k)$ since the probability of the numbers with infinite length be seperated into the intervals. Then since each open interval can be written as a countable union of non-overlapping half-open dyadic intervals, we know from the discussion above that $T(E)$ is measurable, and $m(T(E)) = m(E)$.
